---
title: 'Business Case: Air France'
author: 'Data Science: Machine Learning     |     Team 10     |     MsBA1'
date: "16/02/2021"
output: pdf_document
---
<br><br>

## 1.) Import of Libraries & Data Set
As a first step is important to import all the libraries as well as the data set to make the environment ready...
<br>
```{r import, echo=TRUE, message=FALSE, warning=FALSE}
# Loading the libraries
library(readxl)
library(rstudioapi) 
library(dplyr)
library(plotly)
library(pixiedust)
library(kableExtra)

# Reading the file
AF_df <- read_excel("Air France Case Spreadsheet Supplement.xls",
                    sheet = "DoubleClick")
kayak_df <- read_excel("Air France Case Spreadsheet Supplement.xls",
                    sheet = "Kayak",
                    range = "B8:H9")
```
<br><br>

## 2.) Data Massaging
As a second step we are going to massage our data by masking sure to be aware of missing values, ensuring consistency in your data and the proper structure of the different variables. Additionally our team calculated valuable additional KPIs which we could be derived from the given data.
<br>
``` {r massaging, echo=TRUE, message=FALSE, warning=FALSE}
# Replacing missing values with NA
AF_df[AF_df == "" ] <- NA

# Checking for missing values
sapply(AF_df, function(x) sum(is.na(x)))

# Getting unique values for Publisher Name
publish_unique <- unique(AF_df$`Publisher Name`)

# Evaluating current unique bid strategy values
unique(AF_df$`Bid Strategy`)

# For loop to set bid strategies to a standardized format
for (i in 1:nrow(AF_df)) {
  if(grepl("1-2", AF_df$`Bid Strategy`[i]) == TRUE 
     || grepl("1 -2", AF_df$`Bid Strategy`[i]) == TRUE
     || grepl("1- 2", AF_df$`Bid Strategy`[i]) == TRUE) {
    AF_df$`Bid Strategy`[i] <- "1-2"
  } else if (grepl("1-3", AF_df$`Bid Strategy`[i]) == TRUE 
             || grepl("1 -3", AF_df$`Bid Strategy`[i]) == TRUE
             || grepl("1- 3", AF_df$`Bid Strategy`[i]) == TRUE) {
    AF_df$`Bid Strategy`[i] <- "1-3"
  } else if (grepl("1-4", AF_df$`Bid Strategy`[i]) == TRUE 
             || grepl("1 -4", AF_df$`Bid Strategy`[i]) == TRUE
             || grepl("1- 4", AF_df$`Bid Strategy`[i]) == TRUE) {
    AF_df$`Bid Strategy`[i] <- "1-4"
  } else if (grepl("2-5", AF_df$`Bid Strategy`[i]) == TRUE 
            || grepl("2 -5", AF_df$`Bid Strategy`[i]) == TRUE
            || grepl("2- 5", AF_df$`Bid Strategy`[i]) == TRUE) {
    AF_df$`Bid Strategy`[i] <- "2-5"
  } else if (grepl("3-6", AF_df$`Bid Strategy`[i]) == TRUE 
             || grepl("3 -6", AF_df$`Bid Strategy`[i]) == TRUE
             || grepl("3- 6", AF_df$`Bid Strategy`[i]) == TRUE) {
    AF_df$`Bid Strategy`[i] <- "3-6"
  } else if (grepl("5-10", AF_df$`Bid Strategy`[i]) == TRUE 
             || grepl("5 -10", AF_df$`Bid Strategy`[i]) == TRUE
             || grepl("5- 10", AF_df$`Bid Strategy`[i]) == TRUE) {
    AF_df$`Bid Strategy`[i] <- "5-10"
  } else if (is.na(AF_df$`Bid Strategy`[i]) == TRUE) {
    next
  } else {
    print("WARNING: There are Bid Strategies which weren't converted to a standardized format!")
  }
}

# Transforming bid strategies to a factor with i customized levels
AF_df$`Bid Strategy` <- factor(AF_df$`Bid Strategy`, levels = c("1-2", "1-3", "1-4", "2-5", "3-6", "5-10"))

# Re-evaluating unique bid strategy values
unique(AF_df$`Bid Strategy`)

# Creating Transaction Conversion variable for Kayak
kayak_df <- within(data = kayak_df, `Trans. Conv. %` <- `Total Bookings`/Clicks)

# Creating a Profit Column
AF_df$Profit <- AF_df$Amount - AF_df$`Total Cost`
colnames(kayak_df)[7] <- "Profit" 
# Creating a ROI Column
AF_df <- within(data = AF_df, ROI <- Profit/`Total Cost`)
kayak_df <- within(data = kayak_df, ROI <- Profit/`Media Cost`)
# Creating a ROA Column
AF_df <- within(data = AF_df, ROA <- Amount/`Total Cost`)
kayak_df <- within(data = kayak_df, ROA <- `Total Revenue`/`Media Cost`)


# Creating Columns for Profits per Booking / Cost per Booking / Probability of Booking
AF_df <- within(data = AF_df, Prof_Book <- Profit/`Total Volume of Bookings`)
kayak_df <- within(data = kayak_df, Prof_Book <- Profit/`Total Bookings`)
AF_df <- within(data = AF_df, Cost_Book <- `Total Cost`/`Total Volume of Bookings`)
kayak_df <- within(data = kayak_df, Cost_Book <- `Media Cost`/`Total Bookings`)
AF_df <- within(data = AF_df, Prob_of_Book <- `Trans. Conv. %` * `Engine Click Thru %`/100)

# Replacing infinite values for 0 in the dataset
AF_df[AF_df == "Inf"] <- 0
``` 
<br><br>

## 3.) Descriptive Statistics
<br>
``` {r descriptive, echo=TRUE, message=FALSE, warning=FALSE}
# Creating a UDF to evaluate min, mean, standard deviation and maximum values
stats_udf <- function(x){
  my_min <- round(min(x, na.rm = T),2)
  my_mean <- round(mean(x, na.rm = T),2)
  my_sd <- round(sd(x, na.rm = T),2)
  my_max <- round(max(x, na.rm = T),2)
  return(c(my_min, my_mean, my_sd, my_max))
} # closing my_desc

# Obtaining descriptive statistics for Clicks, Impressions, Amount and Total Costs
Clicks_stats <- stats_udf(AF_df$Clicks)
Impressions_stats <- stats_udf(AF_df$Impressions)
Amount_stats <- stats_udf(AF_df$Amount)
Tot_Cost_stats <- stats_udf(AF_df$`Total Cost`)

# Creating a dataframe with our descriptive statistics obtained
stats_df <- as.data.frame(cbind(Clicks_stats, Impressions_stats, Amount_stats, Tot_Cost_stats))
colnames(stats_df) <- c("Clicks", "Impressions", "Amount", "Total Cost")
rownames(stats_df) <- c("Minimum", "Mean", "Standard Deviation", "Maximum")

# Plotting the data frame
dust(stats_df) %>%
  sprinkle(round = 3) %>%
  kable() %>%
  kable_styling()

# Finding the Sales per Publisher
Sales <- c()
# for loop to find the Publisher Name and obtain the total sales per Publisher
for (i in 1:length(publish_unique)) {#start for loop
  Sales <- c(Sales,sum(AF_df$Amount[which(AF_df[,2] == publish_unique[i])]))
  i <- i + 1
} # end for loop

# Creating a matrix called of the Sales for each Publisher
Sales_Publisher <- data.frame(cbind(publish_unique,as.numeric(Sales)))
# Naming the columns with Publisher Names
colnames(Sales_Publisher)<- c("Publisher", "Sales")

# Plotting the data frame
dust(Sales_Publisher) %>%
  sprinkle(round = 3) %>%
  kable() %>%
  kable_styling()
```
<br><br>

## 4.) Visualizations

<br>

### 4.1.) Some Visualizations: Quick Overview about Publishers
This visualizations helped us to get a quick overview about the different publishers (for now excluding Kayak)

<br>

#### 4.1.1.) Bar Chart of ROA per Publisher
<br>

``` {r visual_roa_pub, echo=TRUE, message=FALSE, warning=FALSE}
#creating the independent variable (Publisher Name) for the graph
publisher_names <- publish_unique
#creating the dependent variable (ROA) for the graph using a for loop
avg_roa <- c()
for (i in 1:length(publish_unique)) {
  mean_roa <- mean(AF_df$ROA[which(AF_df[ , 2] == publish_unique[i])])
  avg_roa <- append(avg_roa, mean_roa)
}
#adding Kayak to our data
publisher_names <- append(publisher_names,'Kayak')
avg_roa <- append(avg_roa, kayak_df$ROA)
#creating a data frame with our data
data <- data.frame(publisher_names, avg_roa )
#plotting the bar chart
data$publisher_names <- factor(data$publisher_names, levels = data[["publisher_names"]])
pub_roa <- plot_ly(data, x= ~publisher_names, y= ~avg_roa, type = "bar",
                   name = "Return on Advertising", color = I("red"), alpha = 0.7,
                   width = 750, height = 500) %>%
  add_text(text = round(avg_roa, digits = 2), textposition = 'top', color = I("black")) %>%
  layout(title = "Return On Advertising",
         xaxis = list(title = ""),
         yaxis = list(title = ""),
         showlegend = FALSE) 
#printing the bar chart
```

<br>

``` {r out.width = "100%", fig.align="center", message=FALSE, warning=FALSE}
pub_roa
```
<br><br>

#### 4.1.2.) Bar Chart of Profit per Publisher
<br>

``` {r visual_prof_pub, echo=TRUE, message=FALSE, warning=FALSE}
#creating the dependent variable (Profit) for the graph using a for loop
avg_profit <- c()
for (i in 1:length(publish_unique)) {
  mean_prof <- mean(AF_df$Profit[which(AF_df[ , 2] == publish_unique[i])])
  avg_profit <- append(avg_profit, mean_prof)
}
#creating a data frame with our data
data <- data.frame(publish_unique, avg_profit)
#plotting the bar chart
data$publish_unique <- factor(data$publish_unique, levels = data[["publish_unique"]])
pub_prof <- plot_ly(data, x= ~publish_unique, y= ~avg_profit, type = "bar", name = "Profit", 
                    color = I("red"), alpha = 0.7,
                    width = 750, height = 500) %>%
  add_text(text = round(avg_profit, digits = 2), textposition = 'top', color = I("black")) %>%
  layout(title = "Profit",
         xaxis = list(title = ""),
         yaxis = list(title = ""),
         showlegend = FALSE)
#printing the bar chart
```

<br>

``` {r out.width = "100%", fig.align="center", message=FALSE, warning=FALSE}
pub_prof
```
<br><br>

#### 4.1.3.) Bar Chart of Prob.of Booking per Publisher
<br>

``` {r visual_prob_pub, echo=TRUE, message=FALSE, warning=FALSE}
#creating the dependent variable (Prob.of Booking) for the graph using a for loop
prob_book <- c()
for (i in 1:length(publish_unique)) {
  mean_prob <- mean(AF_df$Prob_of_Book[which(AF_df[ , 2] == publish_unique[i])])
  prob_book <- append(prob_book, mean_prob)
}
#creating a data frame with our data
data <- data.frame(publish_unique, prob_book*100)
#plotting the bar chart
data$publish_unique <- factor(data$publish_unique, levels = data[["publish_unique"]])
pub_book <- plot_ly(data, x= ~publish_unique, y= ~prob_book*100, type = "bar",
                    name = "Probability of Booking", color = I("red"), alpha = 0.7,
                    width = 750, height = 500) %>%
  add_text(text = round(prob_book, digits = 2), textposition = 'top', color = I("black")) %>%
  layout(title = "Probability of Booking in %",
         xaxis = list(title = ""),
         yaxis = list(title = ""),
         showlegend = FALSE)
#printing the bar chart
```

<br>

``` {r out.width = "100%", fig.align="center", message=FALSE, warning=FALSE}
pub_book
```
<br><br>

### 4.2.) Some Visualizations including Kayak
Some visualizations to better understand the performance of Kayak in comparison to the other publishers.

<br>

#### 4.2.1.) Bar Chart of Profit per Booking per Publisher (incl. Kayak)
<br>

``` {r visual_prof-book_pub, echo=TRUE, message=FALSE, warning=FALSE}
#creating the independent variable (Publisher Name) for the graph
publisher_names_prof<- publish_unique
#creating the dependent variable (Prof.per Booking) for the graph using a for loop
prof_book <- c()
for (i in 1:length(publish_unique)) {
  mean_profb <- mean(AF_df$Prof_Book[which(AF_df[ , 2] == publish_unique[i] & AF_df[ ,'Total Volume of Bookings'] > 0)])
  prof_book <- append(prof_book, mean_profb)
}
#adding Kayak to our data
publisher_names_prof<- append(publisher_names_prof,'Kayak')
prof_book <- append(prof_book,kayak_df$Prof_Book)
#creating a data frame with our data
data <- data.frame(publisher_names_prof, prof_book)
#plotting the bar chart
data$publisher_names_prof <- factor(data$publisher_names_prof, levels = data[["publisher_names_prof"]])
pub_profb <- plot_ly(data, x= ~publisher_names_prof, y= ~prof_book, type = "bar", 
                     name = "Profit per Booking", color = I("red"), alpha = 0.7,
                     width = 750, height = 500) %>%
  add_text(text = round(prof_book, digits = 2), textposition = 'top', color = I("black")) %>%
  layout(title = "Profit per Booking",
         xaxis = list(title = ""),
         yaxis = list(title = ""),
         showlegend = FALSE)
#printing the bar chart
```

<br>

``` {r out.width = "100%", fig.align="center", message=FALSE, warning=FALSE}
pub_profb
```
<br><br>

#### 4.2.2.) Bar Chart of Cost per Booking per Publisher (incl. Kayak)
<br>

``` {r visual_cost-book_pub, echo=TRUE, message=FALSE, warning=FALSE}
#creating the independent variable (Publisher Name) for the graph
publisher_names_cpb <- publish_unique
#creating the dependent variable (Prob.of Booking) for the graph using a for loop
cost_book <- c()
for (i in 1:length(publish_unique)) {
  mean_costb <- mean(AF_df$Cost_Book[which(AF_df[ , 2] == publish_unique[i])])
  cost_book<- append(cost_book, mean_costb)
}
#adding Kayak to our data
publisher_names_cpb <- append(publisher_names_cpb,'Kayak')
cost_book <- append(cost_book, kayak_df$Cost_Book)
#creating a data frame with our data
data <- data.frame(publisher_names_cpb, cost_book)
#plotting the bar chart
data$publisher_names_cpb <- factor(data$publisher_names_cpb, levels = data[["publisher_names_cpb"]])
pub_costb <- plot_ly(data, x= ~publisher_names_cpb, y= ~cost_book, type = "bar", 
                     name = "Cost per Booking", color = I("red"), alpha = 0.7,
                     width = 750, height = 500) %>%
  add_text(text = round(cost_book, digits = 2), textposition = 'top', color = I("black")) %>%
  layout(title = "Cost per Booking",
         xaxis = list(title = ""),
         yaxis = list(title = ""),
         showlegend = FALSE)
#printing the bar chart
```
<br>
``` {r out.width = "100%", fig.align="center", message=FALSE, warning=FALSE}
pub_costb
```
<br><br>

#### 4.2.3.) Bar Chart of Return on Investment per Publisher (incl. Kayak)
<br>

``` {r visual_roi_pub, echo=TRUE, message=FALSE, warning=FALSE}
#creating the independent variable (Publisher Name) for the graph
publisher_names_roip <- publish_unique
#creating the dependent variable (Prob.of Booking) for the graph using a for loop
avg_roi <- c()
for (i in 1:length(publish_unique)) {
  mean_roi <- mean(AF_df$ROI[which(AF_df[ , 2] == publish_unique[i])])
  avg_roi <- append(avg_roi, mean_roi)
}
#adding Kayak to our data
publisher_names_roip <- append(publisher_names_roip,'Kayak')
avg_roi <- append(avg_roi, kayak_df$ROI)
#creating a data frame with our data
data <- data.frame(publisher_names_roip, avg_roi)
#plotting the bar chart
data$publisher_names_roip <- factor(data$publisher_names_roip, levels = data[["publisher_names_roip"]])
pub_roi <- plot_ly(data, x= ~publisher_names_roip, y= ~avg_roi, type = "bar", 
                   name = "Return on investment", color = I("red"), alpha = 0.7,
                   width = 750, height = 500) %>%
  add_text(text = round(avg_roi, digits = 2), textposition = 'top', color = I("black")) %>%
  layout(title = "Return On Investment",
         xaxis = list(title = ""),
         yaxis = list(title = ""),
         showlegend = FALSE)
#printing the bar chart
```

<br>

``` {r out.width = "100%", fig.align="center", message=FALSE, warning=FALSE}
pub_roi
```
<br><br>

#### 4.2.4.) Bar Chart of Transaction Conv.% per Publisher (incl. Kayak)
<br>

``` {r visual_trans-conv_pub, echo=TRUE, message=FALSE, warning=FALSE}
#creating the independent variable (Publisher Name) for the graph
publisher_names_tcp <- publish_unique
#creating the dependent variable (Prob.of Booking) for the graph using a for loop
trans_conv <- c()
for (i in 1:length(publish_unique)) {
  mean_tc <- mean(AF_df$`Trans. Conv. %`[which(AF_df[ , 2] == publish_unique[i])])
  trans_conv <- append(trans_conv,mean_tc)
}
#adding Kayak to our data
publisher_names_tcp <- append(publisher_names_tcp,'Kayak')
trans_conv <- append(trans_conv, kayak_df$`Trans. Conv. %`*100)
#creating a data frame with our data
data <- data.frame(publisher_names_tcp, trans_conv )
#plotting the bar chart
data$publisher_names_tcp <- factor(data$publisher_names_tcp, levels = data[["publisher_names_tcp"]])
pub_tcr <- plot_ly(data, x= ~publisher_names_tcp, y= ~trans_conv , type = "bar", 
                   name = "Transaction Conversion in %", color = I("red"), alpha = 0.7,
                   width = 750, height = 500) %>%
  add_text(text = round(trans_conv, digits = 2), textposition = 'top', color = I("black")) %>%
  layout(title = "Transaction Conversion in %",
         xaxis = list(title = ""),
         yaxis = list(title = ""),
         showlegend = FALSE)
#printing the bar chart
```

<br>

``` {r out.width = "100%", fig.align="center", message=FALSE, warning=FALSE}
pub_tcr
```
<br><br>

### 4.3.) Additional insightful Charts (excl. Kayak)
These are furter insights we investigated on. The data we collected on Kayak provided had information for these ones.

<br>

#### 4.3.1) Bar Chart of Avg. Cost per Click per Publisher
<br>

``` {r visual_cpc_pub, echo=TRUE, message=FALSE, warning=FALSE}
#creating the dependent variable (Prob.of Booking) for the graph using a for loop
avg_cpc <- c()
for (i in 1:length(publish_unique)) {
  mean_avgcpc <- mean(AF_df$`Avg. Cost per Click`[which(AF_df[ , 2] == publish_unique[i])])
  avg_cpc<- append(avg_cpc, mean_avgcpc)
}
#creating a data frame with our data
data <- data.frame(publish_unique, avg_cpc)
#plotting the bar chart
data$publish_unique <- factor(data$publish_unique, levels = data[["publish_unique"]])
pub_cpc <- plot_ly(data, x= ~publish_unique, y= ~avg_cpc, type = "bar", name = "Avg. Cost per Click", 
                   color = I("red"), alpha = 0.7,
                   width = 750, height = 500) %>%
  add_text(text = round(avg_cpc, digits = 2), textposition = 'top', color = I("black")) %>%
  layout(title = "Avg. Cost per Click",
         xaxis = list(title = ""),
         yaxis = list(title = ""),
         showlegend = FALSE)
#printing the bar chart
```
<br>
``` {r out.width = "100%", fig.align="center", message=FALSE, warning=FALSE}
pub_cpc
```
<br><br>

#### 4.3.2.) Bar Chart Click Trough.% per Publisher
<br>

``` {r visual_click-through_pub, echo=TRUE, message=FALSE, warning=FALSE}
#creating the independent variable (Publisher Name) for the graph
publisher_names_ctr<- publish_unique
#creating the dependent variable (Prof.per Booking) for the graph using a for loop
click_tr <- c()
for (i in 1:length(publish_unique)) {
  mean_clickt <- mean(AF_df$`Engine Click Thru %`[which(AF_df[ , 2] == publish_unique[i])],round(2))
  click_tr<- append(click_tr, mean_clickt)
}
#creating a data frame with our data
data <- data.frame(publisher_names_ctr, click_tr)
#plotting the bar chart
data$publisher_names_ctr <- factor(data$publisher_names_ctr, levels = data[["publisher_names_ctr"]])
pub_ctr <- plot_ly(data, x= ~publisher_names_ctr, y= ~click_tr, type = "bar", 
                   name = "Click Through Rate in %", color = I("red"), alpha = 0.7,
                   width = 750, height = 500) %>%
  add_text(text = round(click_tr, digits = 2), textposition = 'top', color = I("black")) %>%
  layout(title = "Click Through Rate in %",
         xaxis = list(title = ""),
         yaxis = list(title = ""),
         showlegend = FALSE)
#printing the bar chart
```

<br>

``` {r out.width = "100%", fig.align="center", message=FALSE, warning=FALSE}
pub_ctr
```
<br><br>

### 4.4.) Visualizations regarding the Power of Branded Keywords
This graphs aim to better understand how well placed branded keywords can significantly contribute to better financial outcomes.
As there were no keywords mentioned in the Kayak sheet - Kayak is not included in these graphs.

<br>

#### 4.4.1.) Bar Chart Probability of Booking by Branded and Unbranded Keywords
<br>

``` {r visual_prob_kw, echo=TRUE, message=FALSE, warning=FALSE}
#creating a vector with branded key words
brand_keys <- c("airfrance", "air france")
#creating a a dataf frame with branded keywords
df_branded <- AF_df[grep(paste(brand_keys, collapse = "|"), AF_df$Keyword, ignore.case = TRUE),]
#creating a a data frame with unbranded keywords
df_not_branded <- AF_df[-grep(paste(brand_keys, collapse = "|"), AF_df$Keyword, ignore.case = TRUE),]
#creating a vector with the mean booking probability of branded and unbranded key words
prob_book_vect <- c(mean(df_branded$Prob_of_Book), mean(df_not_branded$Prob_of_Book))
#creating a vector with the mean profit of branded and unbranded key words
avg_prof_vect <- c(mean(df_branded$Profit), mean(df_not_branded$Profit))
#creating a data frame with probability of booking and profit
df_branded_unbranded <- as.data.frame(cbind(prob_book_vect*100, avg_prof_vect))
#naming the columns of the data frame
colnames(df_branded_unbranded) <- c("Probability of Bookings", "Average Profits")
#naming the rows of the data frame
rownames(df_branded_unbranded) <- c("Branded Keywords", "Unbranded Keywords")

#plotting the bar chart
prob_bk_kw <- plot_ly(data = df_branded_unbranded, x = rownames(df_branded_unbranded), 
                       y= ~`Probability of Bookings`, type = "bar", name = "Probability of Bookings", 
                       color = I("red"), alpha = 0.7,
                       width = 750, height = 500) %>%
  add_text(text = round(prob_book_vect*100, digits = 2), textposition = 'top', color = I("black")) %>%
  layout(title = "Probability of Bookings in %",
         xaxis = list(title = ""),
         yaxis = list(title = ""),
         showlegend = FALSE)
#printing the bar chart
```

<br>

``` {r out.width = "100%", fig.align="center", message=FALSE, warning=FALSE}
prob_bk_kw
```
<br><br>

#### 4.4.2.) Bar Chart Average Profits by Branded and Unbranded Keywords
<br>

``` {r visual_prof_kw, echo=TRUE, message=FALSE, warning=FALSE}
#plotting the bar chart
prof_kw <- plot_ly(df_branded_unbranded, x = rownames(df_branded_unbranded), y= ~`Average Profits`, 
                   type = "bar", name = "Average Profits", color = I("red"), alpha = 0.7,
                   width = 750, height = 500) %>%
  add_text(text = round(avg_prof_vect, digits = 2), textposition = 'top', color = I("black")) %>%
  layout(title = "Average Profits",
         xaxis = list(title = ""),
         yaxis = list(title = ""),
         showlegend = FALSE)
#printing the bar chart
```

<br>

``` {r out.width = "100%", fig.align="center", message=FALSE, warning=FALSE}
prof_kw
```
<br><br>

### 4.5.) Visualizations regarding ROA - SEM - Cost per Click - Probabilities of Booking
These visualizations aim to better understand the correlations between the variables explained above and in particularly looking at them again in terms of the different channels. Without Kayak as there were lacking certain data.

<br>

#### 4.5.1.) Pivot table for ROA and Avg.Cost per Click
<br>

``` {r pivot_roa_cpc, echo=TRUE, message=FALSE, warning=FALSE}
#creating my pivot table
AF_df_ptrc <- AF_df %>% group_by(`Publisher Name`) %>% summarize(
  Avg_ROA = mean(ROA),
  Avg_cpc = mean(`Avg. Cost per Click`)
)
# Plotting the pivot table
dust(AF_df_ptrc) %>%
  sprinkle(round = 3) %>%
  kable() %>%
  kable_styling()
```
<br><br>

#### 4.5.2.) Pivot table for ROA compare different Search Engine Marketing (SEM)
<br>

``` {r pivot_roa_sem, echo=TRUE, message=FALSE, warning=FALSE}
#creating my pivot table
AF_df_ptsem <- AF_df %>% group_by(`Publisher Name`) %>% summarize(
  total_records = n(),
  total_amount = sum(`Total Cost`),
  Avg_cpc = mean(`Avg. Cost per Click`),
  Avg_prob = mean(`Prob_of_Book`),
  Avg_ROA = mean(ROA)
)
# Plotting the pivot table
dust(AF_df_ptsem) %>%
  sprinkle(round = 3) %>%
  kable() %>%
  kable_styling()
```
<br><br>

#### 4.5.3.) Bubble Chart Probability of Booking and Avg.ROA
<br>

``` {r visual_prob-book_roa, echo=TRUE, message=FALSE, warning=FALSE}
#creating my bubble chart
bub_pbr<- plot_ly(AF_df_ptsem, x = ~Avg_prob*100, y = ~Avg_ROA,
             textposition = "auto",
             type = 'scatter', 
             mode = 'markers', 
             size = ~Avg_cpc, 
             color = ~`Publisher Name`, 
             colors = 'Paired',
             marker = list(opacity = 0.8, sizemode = 'diameter'),
             width = 750, height = 500) %>%
  layout(title = 'Cost per Click Bubble Chart',
         xaxis = list(title = "Probability of Booking in %", showgrid = TRUE),
         yaxis = list(title = "Avg. ROA", showgrid = TRUE),
         showlegend = TRUE)
#printing my bubble chart
```

<br>

``` {r out.width = "100%", fig.align="center", message=FALSE, warning=FALSE}
bub_pbr
```
<br><br>

### 4.6.) Visualizations with the subset of existing Bid Strategy
These visualizations aim to get a better understanding about the different Bid Strategies.
Without Kayak as there were lacking data on on Bid Strategy.

<br>

#### 4.6.1.) Creating a pivot table of the subset where a Bid Strategy was defined
<br>

``` {r pivot_bid-sub, echo=TRUE, message=FALSE, warning=FALSE}
# Creating my pivot table
AF_df_ptbs <- (subset(AF_df, is.na(AF_df$`Bid Strategy`) == FALSE) %>%
  group_by(`Publisher Name`, `Bid Strategy`) %>%
  summarize(
    total_records = n(),
    avg_cpc = mean(`Avg. Cost per Click`),
    avg_prof = mean(`Profit`) )
    )
# Plotting the pivot table
dust(AF_df_ptbs) %>%
  sprinkle(round = 3) %>%
  kable() %>%
  kable_styling()
```
<br><br>

#### 4.6.2.) Bubble Chart Avg. Profits in regard to Cost per Click & Bid Strategy
<br>

``` {r visual_prof-cpc-bid, echo=TRUE, message=FALSE, warning=FALSE}
# Creating my bubble chart
bub_pcpcbid <- plot_ly(data = AF_df_ptbs, x = ~`Bid Strategy`, y = ~avg_cpc, 
                       type = "scatter", mode = "markers",
                       color = AF_df_ptbs$`Publisher Name`,
                       colors = c("darkolivegreen", "darkolivegreen3", "darkorange3", 
                                  "darkorchid4", "darkorchid1", "goldenrod3"),
                       size = ~avg_prof,
                       opacity = 0.5,
                       marker = list(sizeref = 0.05, sizemode = "area"),
                       showlegend = TRUE,
                       width = 750, height = 500) %>%
  layout(title = 'Average Profits in regard to Cost per Click & Bid Strategy',
         xaxis = list(title = "Bid Strategy", showgrid = TRUE),
         yaxis = list(title = "Cost per Click", showgrid = TRUE))
# Printing my bubble chart
```

<br>

``` {r out.width = "100%", fig.align="center", message=FALSE, warning=FALSE}
bub_pcpcbid
```
<br><br>

#### 4.6.3.) Creating a pivot table of the subset where a Bid Strategy was defined with focus on Match Type
<br>

``` {r pivot_bid-sub-mt, echo=TRUE, message=FALSE, warning=FALSE}
# Creating my pivot table
AF_df_ptbsms <- (subset(AF_df, is.na(AF_df$`Bid Strategy`) == FALSE) %>%
                   group_by(`Publisher Name`, `Bid Strategy`, `Match Type`) %>%
                   summarise(
                     total_records = n(),
                     avg_cpc = mean(`ROA`))
                 )
# Plotting the pivot table
dust(AF_df_ptbsms) %>%
  sprinkle(round = 3) %>%
  kable() %>%
  kable_styling()
```
<br><br>

#### 4.6.4.) Bubble Chart ROA in regard to Match Type & Bid Strategy
<br>

``` {r visual_roa-mt-bs, echo=TRUE, message=FALSE, warning=FALSE}
# Creating my bubble chart
bub_roamtbs <- plot_ly(data = AF_df_ptbsms, x = ~`Bid Strategy`, y = ~`Match Type`, 
                       type = "scatter", mode = "markers",
                       color = AF_df_ptbsms$`Publisher Name`,
                       colors = c("darkolivegreen", "darkolivegreen3", "darkorange3", 
                                  "darkorchid4", "darkorchid1", "goldenrod3"),
                       size = ~avg_cpc,
                       opacity = 0.5,
                       marker = list(sizeref = 0.02, sizemode = "area"),
                       showlegend = TRUE,
                       width = 750, height = 500) %>%
  layout(title = 'ROA in regard to Match Type & Bid Strategy',
         xaxis = list(title = "Bid Strategy", showgrid = TRUE),
         yaxis = list(title = "Match Type", showgrid = TRUE))

# Printing my bubble chart

# Important to understand that the apparent winner "Google - Global / Match Type: Exact / Bid Strategy: 1-3" consists of only two observations and is therefore not very representative.
```

<br>

``` {r out.width = "100%", fig.align="center", message=FALSE, warning=FALSE}
bub_roamtbs
```
<br><br>

### 4.7.) Visualizations with the subset of existing Bookings
This charts aim to get a better understanding about the situation when it comes to bookings. <br>
Without Kayak as there were lacking certain data.
<br>

#### 4.7.1.) Pivot table of the subset where Bookings occured
<br>

``` {r pivot_book, echo=TRUE, message=FALSE, warning=FALSE}
# Creating my pivot table
AF_df_ptbook <- (subset(AF_df, (AF_df$`Total Volume of Bookings` > 0))) %>%
                   group_by(`Publisher Name`) %>%
                   summarize(
                     count_of_piv = n(),
                     avg_cpc = mean(`Avg. Cost per Click`),
                     avg_cost_book = median(Cost_Book),
                     avg_prob_book = median(Prob_of_Book),
                     avg_prof_book = median(Prof_Book) 
                     )
# Plotting the pivot table
dust(AF_df_ptbook) %>%
  sprinkle(round = 3) %>%
  kable() %>%
  kable_styling()
```
<br><br>

#### 4.7.2.) Bubble Chart Avg. Profits in regards to Prob. of Booking and Cost per Booking
<br>

``` {r visual_prof-probb-cpb, echo=TRUE, message=FALSE, warning=FALSE}
# Creating my bubble chart
bub_ppbcb <- plot_ly(data = AF_df_ptbook, x = ~avg_prob_book, y = ~avg_cost_book, 
               type = "scatter", mode = "markers",
               color = AF_df_ptbook$`Publisher Name`,
               colors = 'Paired',
               size = ~avg_prof_book,
               marker = list(sizeref = 0.05, sizemode = "area"),
               showlegend = TRUE,
               width = 750, height = 500) %>%
  layout(title = 'Avg. Profit p.Booking to Prob. of Booking and Cost per Booking',
         xaxis = list(title = "Probability of Booking", showgrid = TRUE),
         yaxis = list(title = "Costs per Booking", showgrid = TRUE))
# Printing my bubble chart
```

<br>

``` {r out.width = "100%", fig.align="center", message=FALSE, warning=FALSE}
bub_ppbcb
```
<br><br>

#### 4.7.3.) Bubble Chart Avg. Profits per Booking to Probability of Booking and Cost per Click
<br>

``` {r visual_profb-probb-cpc, echo=TRUE, message=FALSE, warning=FALSE}
# Creating my bubble chart
bub_pbpbcc <- plot_ly(data = AF_df_ptbook, x = ~avg_prob_book, y = ~avg_cpc, 
               type = "scatter", mode = "markers",
               color = AF_df_ptbook$`Publisher Name`,
               colors = 'Paired',
               size = ~avg_prof_book,
               marker = list(sizeref = 0.05, sizemode = "area"),
               showlegend = TRUE,
               width = 750, height = 500) %>%
  layout(title = 'Avg Profit p.Booking to Prob. of Booking and Cost per Click',
         xaxis = list(title = "Probability of Booking", showgrid = TRUE),
         yaxis = list(title = "Costs per Click", showgrid = TRUE))
# Printing my bubble chart
```

<br>

``` {r out.width = "100%", fig.align="center", message=FALSE, warning=FALSE}
bub_pbpbcc
```



